### 2012-04-11 tr-semanticsearchsurvey-data/overview.tex

\section{Main Types of Approaches and Their Performances}\label{sec:approaches}	
Semantic search has been investigated from different communities in different contexts. In the IR community, semantic search has mainly been viewed from the perspective of document retrieval. Here, classic \emph{concept}-based approaches based on the use of lexical models can be distinguished from more recent approaches that leverage document \emph{annotations} in the form of semantic data. Another line of research is \emph{entity} search, which has been studied in the context of entities extracted from Web pages, Wikipedia pages corresponding to entities, as well as entities captured by databases and semantic data sources. Another popular topic is keyword search over databases and semantic data, which is mainly about \emph{relational} information. Last but not least, the processing of NL queries over these semantic data entails specific challenges and opportunities, which has attracted interests from a specific community of researchers. We will now discuss these main types of approaches, several example systems, the ways they use semantics, as well as their reported performances. The classification of selected approaches into types is presented in Table~\ref{}. Further, Table~\ref{tab:examples} provides an overview of selected systems and their classification along the main aspects of semantic search discussed in this survey. Since the technique used within the same system is similar for document and query interpretation, we omit this distinction in Table~\ref{tab:examples}.

\dtr{Say what  systems do with respect to aspects}

% Table generated by Excel2LaTeX from sheet 'Tabelle5'
\begin{table*}[htbp]
  \centering
  \caption{Classification of selected approaches into types.}
    \begin{tabular}{|p{2cm}|p{1.5cm}|p{2cm}|p{1.5cm}|p{1.5cm}|p{2cm}|p{2cm}|p{1.5cm}|}
    \hline
    \multicolumn{1}{|c|}{\multirow{2}[4]{*}{Concept-based}} & \multicolumn{2}{c|}{Annotation-based} & \multicolumn{3}{c|}{Entity Search} & \multicolumn{1}{c|}{\multirow{2}[4]{*}{Rel. Keyword}} & \multicolumn{1}{c|}{\multirow{2}[4]{*}{Rel. NL}} \bigstrut\\
\cline{2-6}    \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{NL} & \multicolumn{1}{c|}{Keyword } & \multicolumn{1}{c|}{Document} & \multicolumn{1}{c|}{Wikipedia} & \multicolumn{1}{c|}{Semantic Data} & \multicolumn{1}{c|}{} & \multicolumn{1}{c|}{} \bigstrut\\
    \hline
    \hline
    \cite{DBLP:conf/sigir/Giger88, DBLP:conf/esws/GiunchigliaKZ09, DBLP:conf/sigir/QiuF93, DBLP:conf/trec/TrieschniggKS06, DBLP:conf/trec/TrieschniggKS06, DBLP:conf/trec/ZhouYTS06,  DBLP:journals/ws/JonquetLFCNMS11, DBLP:conf/trec/JelierSEWMSMK03, DBLP:conf/sigir/Voorhees93, DBLP:conf/sigir/Voorhees94, DBLP:journals/ipm/MeijTRK10} & \cite{DBLP:conf/sigir/Chu-CarrollPCFD06, DBLP:journals/tkde/CastellsFV07, DBLP:journals/ws/FernandezCLVCM11, tran2007expressive, DBLP:conf/cikm/Chu-CarrollP07} &  	  \cite{DBLP:journals/tkde/CastellsFV07, DBLP:conf/sigmod/KandoganKRVZ06, tran2007expressive, DBLP:conf/aaai/JiangT06, DBLP:series/sci/NgoC10, DBLP:conf/www/RochaSA04, DBLP:conf/esws/SchumacherSS08, DBLP:conf/www/GuhaMM03} & \cite{DBLP:journals/ipm/BalogAR09, DBLP:conf/cikm/KapteinSVK10, DBLP:conf/sigir/Chu-CarrollPCFD06} & \cite{DBLP:journals/tois/BalogBR11, DBLP:conf/cikm/KapteinSVK10, DBLP:conf/cikm/BronBR10, DBLP:conf/ecir/PehcevskiVT08} & \cite{DBLP:conf/vldb/BalminHP04, DBLP:conf/sigir/BastCSW07, DBLP:conf/semweb/BlancoMV11, DBLP:journals/ijswis/ChengQ09, DBLP:journals/ws/TummarelloCCDDD10, DBLP:conf/eswc/Tran12,DBLP:conf/www/NieMSWM07, DBLP:conf/www/NieZWM05} & \cite{DBLP:conf/vldb/BalminHP04, DBLP:conf/cikm/BicerTN11, DBLP:conf/cikm/CoffmanW11, DBLP:journals/debu/ElbassuoniRSW10, DBLP:journals/ws/TranWH09, DBLP:journals/ws/TranHL11, DBLP:conf/icde/KasneciSIRW08, DBLP:conf/sigmod/LiJLF09, DBLP:conf/cikm/LadwigT11} & \cite{DBLP:conf/aswc/CaoCT08, DBLP:journals/dke/CimianoHHMS08, DBLP:conf/esws/WangXZY07, DBLP:conf/esws/DamljanovicAC10, DBLP:journals/ws/LopezUMP07} \bigstrut\\
    \hline
    \end{tabular}%
  \label{tab:approaches}%
\end{table*}%

\subsection{Concept-based Document Retrieval} This is the classic type of semantic search systems, which has been studied already in the early years of IR research. Researchers have recognized for a richer representation of the information needs and data that goes beyond the bag-of-words model. It became evident that constructing a full-fledge logic-based representation~\cite{DBLP:conf/sigir/Rijsbergen89} for queries and especially for documents is not practical. Thus, lightweight \emph{lexical models} have been employed to interpret the semantics of query and documents as concepts, and used within the standard bag-of-words IR paradigm (e.g. vector space model and language model). In fact, retrieval may be done based on concepts alone, i.e. using bag-of-concepts, or in the form of query and document expansion. In the latter case, bag-of-words model constitutes the basis while the conceptual understanding helps to refine or add more relevant words.

@@

\subsection{Annotation-based Document Retrieval} These approaches exploit the advancement in information extraction technologies to obtain a richer representation of queries and documents, namely as \emph{entities} and \emph{relations} represented as annotations (query and document annotations, respectively). As shown in Table~\ref{tab:approaches}, this query interpretation has has been applied both to keywords and NL questions. 
%That is, this category covers both keyword search and NL question answering over documents.

@@

\subsection{Entity Search} While the two mentioned types retrieve documents, this type of approaches search for entities representing real-world objects (anything objects but documents). It includes search over (1) documents (e.g. for processing entity-related factoid and list queries of the TREC Question Answering track~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06}, or expert search queries of the TREC Enterprise track~\cite{DBLP:journals/ipm/BalogAR09}), 
%\dtr{todo: A particular type of entity search, expert retrieval has been the focus of a number of evaluations; also belong to the type of entity search that mainly operates on documents; + some other features?.} 
(2) over 
%documents associated with metadata, (for answering entity-related queries of the INEX Entity Ranking track~\cite{DBLP:conf/cikm/KapteinSVK10,DBLP:conf/ecir/PehcevskiVT08}), 
%over (3) 
Wikipedia data, which as discussed, can be seen as a kind of semantic data (e.g. for answering entity-related queries of the INEX Entity Ranking track~\cite{DBLP:conf/cikm/KapteinSVK10,DBLP:conf/ecir/PehcevskiVT08}), or over pure (3) semantic data crawled from the Web (e.g. for answering entity queries of the SemSearch Entity track~\cite{DBLP:conf/semweb/BlancoMV11}).

Some type(1) systems can also be categorized as annotation-based document retrieval systems because they detect entities and relations in data and queries~\cite{DBLP:conf/vldb/ChengYC07,DBLP:conf/www/NieMSWM07,DBLP:conf/sigir/Chu-CarrollPCFD06}. However, they go standard beyond document retrieval to locate the parts (passages) in the documents that contain answers to the query. As mentioned in the previous Subsection, the work from IBM~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06} showed that precision can be improved when high quality extraction outputs are available.

The use of semantics in type(2) systems is limited to viewing Wikipedia pages as entities~\cite{DBLP:conf/cikm/KapteinSVK10}, exploiting categories associated with them~\cite{DBLP:journals/tois/BalogBR11} as well as links between them~\cite{DBLP:conf/ecir/PehcevskiVT08}. As a source of semantics, experiments have shown that category information helps to interpret the entity query and to enrich the Wikipedia documents and as a result, to outperform standard text-based retrieval~\cite{DBLP:conf/cikm/KapteinSVK10,DBLP:journals/tois/BalogBR11}. Interestingly, 
%it has been shown that 
Wikipedia articles can also be effectively used as a pivot for entity search on the Web, i.e. not only for answering queries about Wikipedia entities: It contains entities for a large amount of queries as well as cues (e.g. external links), which can be used to find the homepages of entities on the Web, which are referred to by Wikipedia articles~\cite{DBLP:conf/cikm/KapteinSVK10}.

While many type(3) systems~\cite{DBLP:journals/ijswis/ChengQ09,DBLP:journals/ws/HoganHUKPD11,DBLP:journals/ws/TummarelloCCDDD10,DBLP:journals/ws/TranWH09} have been built to search for entities over semantic data from the Web, solutions for ranking and the evaluation of their results have attracted interest only recently. The first systems (e.g. Falcons) simply used an underlying IR engine (Lucene) to index entities as documents and the built-in mechanism to rank entities. Recently, the SemSearch challenge attracted a large number of participants, which submitted results produced by different ranking schemes based on traditional IR concepts. To date, the best performed method~\cite{DBLP:conf/semweb/BlancoMV11} uses an adoption of BM25F. 
%, which ranks entities as documents that are segmented into different fields corresponding to entity attributes.

\textbf{Examples:}
Systems searching for entity related information extracted from documents include \emph{AVATAR}, \emph{Powerset} and \emph{Watson}. Targeting Wikipedia documents, \emph{SERWi}~\footnote{\url{http://godzilla.kbs.uni-hannover.de:8089/ER08Demo/}} (SER) runs on top of subsets used at INEX XER 2007 and 2008. It exploits category information treated as part of a knowledge model to interpret entity queries expressed as keywords, and returns a ranked list of entities represented by their Wikipedia pages. For the semantic data case, we have \emph{Sig.ma} as one representative system, which provides keyword querying capabilities over an index of semantic data sources. For query answering, it matches query terms against an inverted index of entity descriptions, presents the sources for which matches could be found, and also, allow users to approve or reject certain sources of information. As illustrated in Fig.~\ref{fig:screenshot_yahoo}, Yahoo! (Y!) also employs semantic data for entity search. It uses its own curated sources of semantic data (e.g. data about companies) to provide -- in addition to relevant Web pages -- specific information about the requested entity and links to related entities. Microsoft's \emph{EntityCube} (MS) extracts information from text~\cite{DBLP:conf/www/ZhuNLZW09} to support entity-related keyword queries over documents and extracted information. For every query, it displays matching documents and entity information, and allows users to refine results based on facets representing related entities. As opposed to Yahoo!, which uses BM25F for ranking~\cite{DBLP:conf/semweb/BlancoMV11}, it uses language models for query-relevance~\cite{DBLP:conf/www/NieMSWM07} and also, PopRank for centrality-based ranking~\cite{DBLP:conf/www/NieZWM05}.

\subsection{Relational Keyword Search}
This category comprises all approaches, which process keyword queries over semantic data~\cite{DBLP:conf/icde/TranWRC09,DBLP:conf/cikm/LadwigT11,DBLP:conf/sigmod/LiOFWZ08}. While the results here include entities, the focus is to find possibly complex subgraphs encompassing several entities and relations between them (i.e. to support relational search). There exists a variety of indexing strategies and traversal algorithms that help to perform this task more efficiently. However, recent work~\cite{DBLP:conf/cikm/CoffmanW10} has shown that the proposed ranking strategies (e.g. ~\cite{DBLP:conf/icde/TranWRC09,DBLP:conf/sigmod/LiuYMC06}) based on the adoption of proximity, TFIDF and PageRank do not perform well when considering a broad range of queries. This work aims at a standardized framework and benchmark for evaluating the effectiveness of relational keyword search approaches. Based on this benchmark, it has been shown that high quality results can be achieved through the use of edge-specific language models that are constructed for results and queries~\cite{DBLP:conf/cikm/BicerTN11}. Also, the learning to rank strategy, which combines TFIDF-based ranking, proximity and other factors yields high performance~\cite{DBLP:conf/cikm/CoffmanW11}.

\textbf{Examples:} \emph{AVATAR} in fact, not only can search over annotations but any kinds of semantic data. The structured queries AVATAR obtains from keywords may also involve relational information. Another system is \emph{SemSearchPro} (SPro), which exploits semantics throughout the search process: It uses lexical and knowledge models as well as the semantic data to translate keyword queries to SPARQL queries (interpretation), to find connections between entities mentioned in the keyword query and for processing fully structured SPARQL queries (matching), and to rank results based on structure-based proximity, centrality and query-relevance (ranking). As illustrated in Fig.~\ref{fig:screenshot_iwb}, it also supports faceted search, and iterative query construction where users can iteratively build complexer queries by selecting suggested terms and query completions as they type. TASTIER~\footnote{\url{http://tastier.ics.uci.edu/}} also supports this auto-completion search, suggesting results as users type. The relational search demo is available for DBLP~\footnote{\url{http://dblp.ics.uci.edu/}}, a dataset containing information about entities in the bibliographic domain.

\subsection{Relational NL Search} \dtr{are there benchmarks for NL QA over data?}
As opposed to NL search over documents (mainly studied by IR researchers), this topic attracts a separate community that deals with interfaces over databases and knowledge bases (expert systems). NL search

\textbf{Example:}
Ask Gianluca, Sig.ma~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06}, Yahoo!

Possibly, the most conclusive result in this direction is based on experiments using the TREC Question Answering track: For a subset of manually chosen questions, it has been shown that higher precision could be obtained~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06}.

@@

    \begin{tabular}{rrcccccccccccccc}
    \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{2}{c}{Concept} & \multicolumn{2}{c}{Annotation} & \multicolumn{5}{c}{Entity}            & \multicolumn{3}{c}{Rel. Keyword} & \multicolumn{2}{c}{Rel. NL} & \\
    \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & NCBO  & C-S.  & Avatar & Aqua* & Exp   & Falc. & Sig.  & Yah.! & E.Cube & S.Pro & Naga  & TAST. & Aqua. & Nalix \\
    \multicolumn{1}{l}{\multirow{3}[0]{*}{Need}} & \multicolumn{1}{l}{Document} & X     &       &       &       &       &       &       & X     &       &       &       &       &       &  \\
    \multicolumn{1}{l}{} & \multicolumn{1}{l}{Entity} &       &       &       &       &       & X     & X     & X     &       &       & X     &       &       &  \\
    \multicolumn{1}{l}{} & \multicolumn{1}{l}{Relation} &       &       &       &       &       &       &       &       &       &       & X     &       &       &  \\
    \multicolumn{1}{l}{\multirow{4}[0]{*}{Querying}} & \multicolumn{1}{l}{Keyword} & X     &       &       &       &       & X     & X     & X     &       &       & ?     &       &       &  \\
    \multicolumn{1}{l}{} & \multicolumn{1}{l}{NL} &       &       &       &       &       &       &       &       &       &       &       &       &       &  \\
    \multicolumn{1}{l}{} & \multicolumn{1}{l}{Facet} & X     &       &       &       &       &       & ?     & X     &       &       &       &       &       &  \\
    \multicolumn{1}{l}{} & \multicolumn{1}{l}{Iterative} & X     &       &       &       &       &       &       &       &       &       &       &       &       &  \\
    \multicolumn{1}{l}{\multirow{3}[0]{*}{Data}} & \multicolumn{1}{l}{Text} & X     &       &       &       &       &       &       & X     &       &       &       &       &       &  \\
    \multicolumn{1}{l}{} & \multicolumn{1}{l}{Sem. Data} &       &       &       &       &       & X     &       & X     &       &       & X     &       &       &  \\
    \multicolumn{1}{l}{} & \multicolumn{1}{l}{Metadata} & X     &       &       &       &       &       &       & X     &       &       &       &       &       &  \\
    \multicolumn{1}{l}{\multirow{2}[0]{*}{Sem. Model}} & \multicolumn{1}{l}{Lexical} & X     &       &       &       &       &       &       &       &       &       &       &       &       &  \\
    \multicolumn{1}{l}{} & \multicolumn{1}{l}{Knowledge} &       &       &       &       &       &       &       &       &       &       &       &       &       &  \\
    \multicolumn{1}{l}{\multirow{3}[0]{*}{Content Int.}} & \multicolumn{1}{l}{Concept} & X     &       &       &       &       &       &       &       &       &       &       &       &       &  \\
    \multicolumn{1}{l}{} & \multicolumn{1}{l}{Entity} &       &       &       &       &       &       &       &       &       &       &       &       &       &  \\

>>>>

\section{Main Types of Approaches and Their Performances}\label{sec:approaches}	
Semantic search has been investigated from different communities in different contexts. In the IR community, semantic search has mainly been viewed from the perspective of document retrieval. Here, classic \emph{concept}-based approaches based on the use of lexical models can be distinguished from more recent approaches that leverage document \emph{annotations} in the form of semantic data. Another line of research is \emph{entity} search, which has been studied in the context of entities extracted from Web pages, Wikipedia pages corresponding to entities, as well as entities captured by databases and semantic data sources. Another popular topic is keyword search over databases and semantic data, which is mainly about \emph{relational} information. Last but not least, the processing of NL queries over these semantic data entails specific challenges and opportunities, which has attracted interests from a specific community of researchers.

Accordingly, we distinguish approaches into five main types, namely concept-based document retrieval, annotation-based document retrieval, entity search, relational keyword search and relational NL search. These types are introduced to represent main communities, which may overlap in some aspects such that some approaches may be classified to multiple types. For instance, an entity search system may use documents and annotations, which would also characterize it as annotation-based search. Most relational search systems also support entity search.

We will now discuss these main types of approaches, several example systems, and their reported performances. The classification of selected approaches into types is presented in Table~\ref{}. Further, Table~\ref{tab:examples} provides an overview of selected systems and their classification along the main aspects of semantic search discussed in this survey.

%Since the technique used within the same system is similar for document and query interpretation, we omit this distinction in Table~\ref{tab:examples}.

% Table generated by Excel2LaTeX from sheet 'Tabelle5'
\begin{table*}[htbp]
  \centering
  \caption{Classification of selected approaches into types.}
    \begin{tabular}{|p{2cm}|p{1.5cm}|p{2cm}|p{1.5cm}|p{1.5cm}|p{2cm}|p{2cm}|p{1.5cm}|}
    \hline
    \multicolumn{1}{|c|}{\multirow{2}[4]{*}{Concept-based}} & \multicolumn{2}{c|}{Annotation-based} & \multicolumn{3}{c|}{Entity Search} & \multicolumn{1}{c|}{\multirow{2}[4]{*}{Rel. Keyword}} & \multicolumn{1}{c|}{\multirow{2}[4]{*}{Rel. NL}} \bigstrut\\
\cline{2-6}    \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{NL} & \multicolumn{1}{c|}{Keyword } & \multicolumn{1}{c|}{Document} & \multicolumn{1}{c|}{Wikipedia} & \multicolumn{1}{c|}{Semantic Data} & \multicolumn{1}{c|}{} & \multicolumn{1}{c|}{} \bigstrut\\
    \hline
    \hline
    \cite{DBLP:conf/sigir/Giger88, DBLP:conf/esws/GiunchigliaKZ09, DBLP:conf/sigir/QiuF93, DBLP:conf/trec/TrieschniggKS06, DBLP:conf/trec/TrieschniggKS06, DBLP:conf/trec/ZhouYTS06,  DBLP:journals/ws/JonquetLFCNMS11, DBLP:conf/trec/JelierSEWMSMK03, DBLP:conf/sigir/Voorhees93, DBLP:conf/sigir/Voorhees94, DBLP:journals/ipm/MeijTRK10} & \cite{DBLP:conf/sigir/Chu-CarrollPCFD06, DBLP:journals/tkde/CastellsFV07, DBLP:journals/ws/FernandezCLVCM11, tran2007expressive, DBLP:conf/cikm/Chu-CarrollP07} &  	  \cite{DBLP:journals/tkde/CastellsFV07, DBLP:conf/sigmod/KandoganKRVZ06, tran2007expressive, DBLP:conf/aaai/JiangT06, DBLP:series/sci/NgoC10, DBLP:conf/www/RochaSA04, DBLP:conf/esws/SchumacherSS08, DBLP:conf/www/GuhaMM03} & \cite{DBLP:journals/ipm/BalogAR09, DBLP:conf/cikm/KapteinSVK10, DBLP:conf/sigir/Chu-CarrollPCFD06} & \cite{DBLP:journals/tois/BalogBR11, DBLP:conf/cikm/KapteinSVK10, DBLP:conf/cikm/BronBR10, DBLP:conf/ecir/PehcevskiVT08} & \cite{DBLP:conf/vldb/BalminHP04, DBLP:conf/sigir/BastCSW07, DBLP:conf/semweb/BlancoMV11, DBLP:journals/ijswis/ChengQ09, DBLP:journals/ws/TummarelloCCDDD10, DBLP:conf/eswc/Tran12,DBLP:conf/www/NieMSWM07, DBLP:conf/www/NieZWM05} & \cite{DBLP:conf/vldb/BalminHP04, DBLP:conf/cikm/BicerTN11, DBLP:conf/cikm/CoffmanW11, DBLP:journals/debu/ElbassuoniRSW10, DBLP:journals/ws/TranWH09, DBLP:journals/ws/TranHL11, DBLP:conf/icde/KasneciSIRW08, DBLP:conf/sigmod/LiJLF09, DBLP:conf/cikm/LadwigT11} & \cite{DBLP:conf/aswc/CaoCT08, DBLP:journals/dke/CimianoHHMS08, DBLP:conf/esws/WangXZY07, DBLP:conf/esws/DamljanovicAC10, DBLP:journals/ws/LopezUMP07, DBLP:journals/tods/LiYJ07, DBLP:conf/iui/HanNPPL10} \bigstrut\\
    \hline
    \end{tabular}%
  \label{tab:approaches}%
\end{table*}%

\subsection{Concept-based Document Retrieval} 
As indicated by example systems shown in Table~\ref{tab:examples}, this type supports keyword search over documents, and based on concepts interpreted from keywords and documents, it may also provide additional querying mechanisms such as as concept-based iterative query construction. In fact, this is the classic type of semantic search systems, which has been studied already in the early years of IR research. Researchers have recognized for a richer representation of the information needs and data that goes beyond the bag-of-words model. It became evident that constructing a full-fledge logic-based representation~\cite{DBLP:conf/sigir/Rijsbergen89} for queries and especially for documents is not practical. Thus, lightweight \emph{lexical models} have been employed to interpret the semantics of query and documents as concepts, and used within the standard bag-of-words IR paradigm (e.g. vector space model and language model). In fact, retrieval may be done based on concepts alone, i.e. using bag-of-concepts, or in the form of query and document expansion. In the latter case, bag-of-words model constitutes the basis while the conceptual understanding helps to refine or add more relevant words.

@@

\subsection{Annotation-based Document Retrieval} These approaches exploit the advancement in information extraction technologies to obtain a richer representation of queries and documents, namely as \emph{entities} and \emph{relations} represented as \emph{annotations} (query and document annotations, respectively). As shown in Table~\ref{tab:approaches}, this query interpretation has has been applied both to keywords and NL questions. 
%That is, this category covers both keyword search and NL question answering over documents.

@@

\subsection{Entity Search} While the two mentioned types retrieve documents, this type of approaches search for \emph{entities} representing real-world objects (anything but documents). It includes search over (1) documents (e.g. for processing entity-related factoid and list queries of the TREC Question Answering track~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06}, or expert search queries of the TREC Enterprise track~\cite{DBLP:journals/ipm/BalogAR09}), 
%\dtr{todo: A particular type of entity search, expert retrieval has been the focus of a number of evaluations; also belong to the type of entity search that mainly operates on documents; + some other features?.} 
(2) over 
%documents associated with metadata, (for answering entity-related queries of the INEX Entity Ranking track~\cite{DBLP:conf/cikm/KapteinSVK10,DBLP:conf/ecir/PehcevskiVT08}), 
%over (3) 
Wikipedia data, which as discussed, can be seen as a kind of semantic data (e.g. for answering entity-related queries of the INEX Entity Ranking track~\cite{DBLP:conf/cikm/KapteinSVK10,DBLP:conf/ecir/PehcevskiVT08}), or over pure (3) semantic data crawled from the Web (e.g. for answering entity queries of the SemSearch Entity track~\cite{DBLP:conf/semweb/BlancoMV11}).

Some \emph{type(1)} systems can also be categorized as annotation-based document retrieval systems because they detect entities and relations in data and queries~\cite{DBLP:conf/vldb/ChengYC07,DBLP:conf/www/NieMSWM07,DBLP:conf/sigir/Chu-CarrollPCFD06}. However, they go standard beyond document retrieval to locate the parts (passages) in the documents that contain answers to the query. As mentioned in the previous Subsection, the work from IBM~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06} showed that precision can be very high when quality extraction outputs are available.

The use of semantics in \emph{type(2)} systems is limited to viewing Wikipedia pages as entities~\cite{DBLP:conf/cikm/KapteinSVK10}, exploiting categories associated with them~\cite{DBLP:journals/tois/BalogBR11} as well as links between them~\cite{DBLP:conf/ecir/PehcevskiVT08}. As a source of semantics, experiments have shown that category information helps to interpret the entity query and to enrich the Wikipedia documents and as a result, to outperform standard text-based retrieval~\cite{DBLP:conf/cikm/KapteinSVK10,DBLP:journals/tois/BalogBR11}. Interestingly, 
%it has been shown that 
Wikipedia articles can also be effectively used as a pivot for entity search on the Web, i.e. not only for answering queries about Wikipedia entities: It contains entities for a large amount of queries as well as cues (e.g. external links), which can be used to find the homepages of entities on the Web, which are referred to by Wikipedia articles~\cite{DBLP:conf/cikm/KapteinSVK10}.

While many \emph{type(3)} systems~\cite{DBLP:journals/ijswis/ChengQ09,DBLP:journals/ws/HoganHUKPD11,DBLP:journals/ws/TummarelloCCDDD10,DBLP:journals/ws/TranWH09} have been built to search for entities over semantic data from the Web, solutions for ranking and the evaluation of their results have attracted interest only recently. The first systems (e.g. Falcons) simply used an underlying IR engine (Lucene) to index entities as documents and the built-in mechanism to rank entities. Recently, the SemSearch challenge attracted a large number of participants, which submitted results produced by different ranking schemes based on traditional IR concepts. To date, the best performed method~\cite{DBLP:conf/semweb/BlancoMV11} uses an adoption of BM25F. 
%, which ranks entities as documents that are segmented into different fields corresponding to entity attributes.

\textbf{Examples:}
Systems searching for entity related information extracted from documents include \emph{AVATAR}, \emph{Powerset} and \emph{Watson}. Targeting Wikipedia documents, \emph{SERWi}~\footnote{\url{http://godzilla.kbs.uni-hannover.de:8089/ER08Demo/}} (SER) runs on top of subsets used at INEX XER 2007 and 2008. It exploits category information treated as part of a knowledge model to interpret entity queries expressed as keywords, and returns a ranked list of entities represented by their Wikipedia pages. For the semantic data case, we have \emph{Sig.ma} as one representative system, which provides keyword querying capabilities over an index of semantic data sources. For query answering, it matches query terms against an inverted index of entity descriptions, presents the sources for which matches could be found, and also, allow users to approve or reject certain sources of information. As illustrated in Fig.~\ref{fig:screenshot_yahoo}, \emph{Yahoo!} (Y!) also employs semantic data for entity search. It uses its own curated sources of semantic data (e.g. data about companies) to provide -- in addition to relevant Web pages -- specific information about the requested entity and links to related entities. Microsoft's \emph{EntityCube} (MS) extracts information from text~\cite{DBLP:conf/www/ZhuNLZW09} to support entity-related keyword queries over documents and extracted information. For every query, it displays matching documents and entity information, and allows users to refine results based on facets representing related entities. As opposed to Yahoo!, which uses BM25F for ranking~\cite{DBLP:conf/semweb/BlancoMV11}, it uses language models for query-relevance~\cite{DBLP:conf/www/NieMSWM07} and also, PopRank for centrality-based ranking~\cite{DBLP:conf/www/NieZWM05}.

\subsection{Relational Keyword Search}
This category comprises all approaches, which process \emph{keyword queries over semantic data} (or structured data capturing entities and relations)~\cite{DBLP:conf/icde/TranWRC09,DBLP:conf/cikm/LadwigT11,DBLP:conf/sigmod/LiOFWZ08}. While the results here include entities, the focus is to find possibly complex subgraphs encompassing several entities and relations between them (i.e. to support relational search). There exists a variety of indexing strategies and traversal algorithms that help to perform this task more efficiently. However, regarding result quality, recent work~\cite{DBLP:conf/cikm/CoffmanW10} has shown that the proposed ranking strategies (e.g. ~\cite{DBLP:conf/icde/TranWRC09,DBLP:conf/sigmod/LiuYMC06}) based on the adoption of proximity, TFIDF and PageRank do not perform well when considering a broad range of queries. This work aims at a standardized framework and benchmark for evaluating the effectiveness of relational keyword search approaches. Based on this benchmark, it has been shown that high quality results can be achieved through the use of edge-specific language models that are constructed for results and queries~\cite{DBLP:conf/cikm/BicerTN11}. Also, the learning to rank strategy, which combines TFIDF-based ranking, proximity and other factors yields high performance~\cite{DBLP:conf/cikm/CoffmanW11}.

\textbf{Examples:} \emph{AVATAR} in fact, not only can search over annotations but any kinds of semantic data. The structured queries AVATAR obtains from keywords may also involve relational information. Another system is \emph{SemSearchPro} (SPro), which exploits semantics throughout the search process: It uses lexical and knowledge models as well as the semantic data to translate keyword queries to SPARQL queries (interpretation), to find connections between entities mentioned in the keyword query and for processing fully structured SPARQL queries (matching), and to rank results based on structure-based proximity, centrality and query-relevance (ranking). As illustrated in Fig.~\ref{fig:screenshot_iwb}, it also supports faceted search, and iterative query construction where users can iteratively build complexer queries by selecting suggested terms and query completions as they type. \emph{TASTIER}~\footnote{\url{http://tastier.ics.uci.edu/}} (TAST) also supports this auto-completion search, suggesting results as users type. The relational search demo is available for DBLP~\footnote{\url{http://dblp.ics.uci.edu/}}, a dataset containing information about entities in the bibliographic domain.

\subsection{Relational NL Search} As opposed to NL search over documents, which is mainly studied by IR researchers, this topic attracts a separate community that deals with interfaces over databases and knowledge bases. The underlying problem is about \emph{searching over semantic data}. We refer to it as relational NL search because relations in the data have to be processed to answer complex queries, possibly asking for relations between several entities. Just like relational keyword search, this type targets the more general relational search scenario, i.e. it can handle the entity query case, while it is not necessarily optimized for it, as opposed to entity search systems.

Traditionally, this query interface is used for expert systems targeting one particular domain.  The question of portability, and the problem of building domain-independent search systems have attracted attention in the past few years~\cite{DBLP:conf/esws/WangXZY07,DBLP:journals/dke/CimianoHHMS08,DBLP:conf/aaai/LiCYSJ07}. While this problem of open-domain NL search, e.g. NL search NL over large amounts of heterogeneous Web data, seems to be largely unsolved, relatively good results have been reported for single domain tasks. However, while there is TREC-based evaluation for NL search over documents, there exists no such thing close to a standardized evaluation in this community. The performances reported by previous approaches are hardly comparable because different queries and datasets have been chosen for the experiments, e.g. experimental settings in recent works~\cite{DBLP:conf/esws/DamljanovicAC10,DBLP:conf/iui/HanNPPL10,DBLP:journals/tods/LiYJ07} differ.

\textbf{Example:} \emph{NaLIX}~\cite{DBLP:journals/tods/LiYJ07} (NaL) is a system built by IBM researchers that was initially focused on one domain and then extended to \emph{DaNaLIX}~\cite{DBLP:conf/aaai/LiCYSJ07} to deal with multiple domains. It interprets a NL query by producing a parse tree and then maps its elements to structured queries via rules. These mapping rules are manually specified and additionally, can be derived from user feedbacks. \emph{Wolfram Alpha} (WolfA) also interprets NL inputs via rules. Its specialty is the ability of computing additional information from the data and results. \emph{True Knowledge} (TrueK) also makes use of reasoning for processing questions and computing results, geospatial and temporal in particular.

@@

    \begin{tabular}{|r|r||c|c|r|c|c|c|c|c|c|c|c|c|c|r|}
    \hline
    \multicolumn{1}{|c}{} & \multicolumn{1}{c||}{} & \multicolumn{2}{c|}{Concept} & \multicolumn{2}{c|}{Annotation} &       & \multicolumn{4}{c|}{Entity}   & \multicolumn{2}{c|}{Rel. Keyword} & \multicolumn{3}{c|}{Rel. NL}   \bigstrut\\
\cline{3-16}    \multicolumn{1}{|c}{} & \multicolumn{1}{c||}{} & NCBO  & Hak   & \multicolumn{1}{c|}{AVA} & PS    & J!    & SER   & Sig.  & Y!    & MS    & SPro  & TAST  & NaL   & WolfA & \multicolumn{1}{c|}{TrueK} \bigstrut\\
    \hline
    \hline
    \multicolumn{1}{|l|}{\multirow{3}[6]{*}{Need}} & \multicolumn{1}{l||}{Document} & X     & X     & X     & X     &       & X     &       & X     & X     &       &       &       &       &  \bigstrut\\
\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{Entity} &       &       & X     & X     & X     & X     & X     & X     & X     & X     & X     & X     & X     & \multicolumn{1}{c|}{X} \bigstrut\\
\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{Relation} &       &       & X     & X     &       &       &       &       &       & X     & X     & X     & X     & \multicolumn{1}{c|}{X} \bigstrut\\
    \hline
    \multicolumn{1}{|l|}{\multirow{4}[8]{*}{Querying}} & \multicolumn{1}{l||}{Keyword} & X     & X     & X     & X     &       & X     & X     & X     & X     & X     & X     &       & X     & \multicolumn{1}{c|}{X} \bigstrut\\
\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{NL} &       & X     &       & X     & X     &       &       &       &       &       &       & X     & X     & \multicolumn{1}{c|}{X} \bigstrut\\
\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{Facet} & X     &       &       &       &       &       &       & X     & X     & X     &       &       &       &  \bigstrut\\
\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{Iterative} & X     &       &       &       &       &       &       &       &       & X     & X     &       &       &  \bigstrut\\
    \hline
    \multicolumn{1}{|l|}{\multirow{3}[6]{*}{Data}} & \multicolumn{1}{l||}{Text} & X     & X     &       & X     & X     & X     &       & X     & X     &       &       &       &       &  \bigstrut\\
\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{Sem. Data} &       &       & X     &       & X     & X     & X     &       &       & X     & X     & X     & X     & \multicolumn{1}{c|}{X} \bigstrut\\
\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{Metadata} & X     & X     & X     & X     & X     &       &       & X     & X     &       &       &       &       &  \bigstrut\\
    \hline
